### 2016-02-23 FCCreport/HH4b.tex
work on the FCC contribution

The results for the signal significance $S/\sqrt{B}$ and
the signal over background ratio
$S/B$ at a 100 TeV collider as a function of the ANN output cut $y_{\rm cut}$
for the three categories are shown in 
Fig.~\ref{fig:sb_mva}.
%
We have assumed a total integrated luminosity of $\mathcal{L}=10$ ab$^{-1}$.
%
The values 
for $y_{\rm cut}=0$ correspond to those at
the end of the loose cut-based analysis.
%
We observe how in the three
 categories there is a marked  improvement in signal
significance as compared to the pre-MVA results.
%
We also observe a substantial enhancement in $S/B$, arising
from the background suppression achieved by the MVA.
%
This improvement in $S/B$ is crucial to ensure the feasibility
of this measurement, since it allows systematic
uncertainties in the background determination to
be at most of a similar size.

@@

%
We find that
in the boosted category, for a value $y_{\rm cut}\simeq $
we end up with around $bbb$ signal events and $aaa$ background
events.
%
Similar results are obtained in the intermediate and resolved
categories: in the former we find aaa ($bbb$) signal (background)
events for $y_{\rm cut}\simeq $ (), and in the latter
$aaa$ ($bbb$) signal (background) events for
$y_{\rm cut}\simeq$.
%
Combining the three categories, taking into
account all background components, we obtain for
$\mathcal{L}=10$ ab$^{-1}$ an overall signal
significance of $S/\sqrt{B}\simeq$.
%
This is a substantial improvement over the corresponding
estimator at 14 TeV, where it was found that for an integrated
luminosity of $\mathcal{L}=3$ ab$^{-1}$ the signal significance was ...

\paragraph{Extracting the Higgs self-coupling.}
%
The extraction of the trilinear coupling $\lambda$ from the
  corresponding cross-section is complicated by the
  destructive interference
  between diagrams that depend on $\lambda$ and those that do not.
  %
 Here we provide a first estimate of the accuracy
  in Higgs self-coupling extraction from the $b\bar{b}b\bar{b}$ final state
  that can be achieved at a 100 TeV hadron collider.
  %
  A robust estimate  would require
  a careful study of the impact of
  experimental systematic uncertainties, which is beyond the scope of this contribution.
  %
  Therefore, we will use a number of simplifying assumptions, in particular
  a very simple estimate of the total systematic uncertainty in the cross-section
  measurement, the limiting factor in the extraction of $\lambda$.

  The sensitivity in the Higgs self-coupling is defined by the $\chi^2$ estimator
  \be
  \label{eq:chi2profile}
  \chi^2(\lambda) \equiv \frac{\lc \sigma(hh,\lambda) - \sigma(hh,\lambda_{\rm SM})
    \rc^2}{\lp \delta_{\rm stat}\sigma\rp^2+\lp \delta_{\rm sys}\sigma\rp^2 } \, ,
  \ee
  where $\lambda$ is the Higgs
  self-coupling, $\lambda_{\rm SM}$ is the SM value, $\sigma(hh,\lambda)$ is the
  post-MVA signal cross-section for a given value of $\lambda$, and $\delta_{\rm stat}\sigma$ and
  $\delta_{\rm sys}\sigma$ are respectively the statistical and systematic uncertainties in the cross-section
  measurement.
  %
  Signal samples for a range of $\lambda$ values have been  processed
  by the same analysis chain, including the MVA (which is not
  retrained), than the SM samples.
  %
  The 68\% CL range for the extraction of $\lambda$ can then be found using
  the usual parameter-fitting criterion by determining the values $\pm \delta\lambda$
  for which the cross-section satisfies
  \be
  \label{eq:condition}
\chi^2(\lambda_{\rm SM}~^{+\delta\lambda}_{-\delta\lambda})=\chi^2(\lambda_{\rm SM})+1 \, .
\ee
%
We explore different assumptions on the value of the total systematic uncertainty $\delta_{\rm sys}\sigma$.
%
The final result for the accuracy in the trilinear extraction is obtained by combining
in quadrature the separate results
from the three exclusive categories.

In Fig.~\ref{fig:chi2} we show the $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section at
  various steps of the cut-flow, including after $b$-tagging
  (before MVA) and after the MVA, in the resolved (left plot)
  and boosted (right plot) categories, as  as a function of the Higgs self-coupling
  $\lambda/\lambda_{\rm SM}$ in units of the SM coupling.
  %
  Imposing the condition Eq.~(\ref{eq:condition}), and combining the
  results of the three categories, we obtain
  that at the 68\% CL we can constrain the
  Higgs trilinear to be ....

@@

\begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|}
    \hline
  $\lc \lambda_{\rm min}/\lambda_{\rm SM},\lambda_{\rm max}/\lambda_{\rm SM} \rc$  &  $\delta_{\rm sys}=25\%$ & $\delta_{\rm sys}=100\%$ \\
    \hline
    \hline
Boosted   & $\lc -0.1, 2.2\rc$  & $\lc -1.5, > 9\rc$  \\
\hline
Intermediate   & $\lc 0.7, 1.6\rc$  &  $\lc -0.4, > 9\rc$  \\
\hline
Resolved   & $\lc 0.9, 1.5\rc$  &  $\lc -0.1, 7\rc$  \\
\hline
  \end{tabular}
  \caption{\label{tab:chi2} The 68\% confidence level intervals
    on the Higgs self-coupling $\lambda_{\rm min}/\lambda_{\rm SM}$ obtained from the condition
    Eq.~(\ref{eq:condition}) in the boosted, resolved and intermediate categories.
    %
    We consider two different assumptions on the total systematic error in the measured
    cross-section,  $\delta_{\rm sys}=25\%$ and $\delta_{\rm sys}=100\%$.
  }
  \end{table}

\paragraph{Summary.} In this contribution we have performed a first exploration of the accuracy that can be expected
for the extraction of the Higgs self-couplings at a 100 TeV hadron collider using the $b\bar{b}b\bar{b}$ final state.

>>>>

The results for the signal significance $S/\sqrt{B}$ and
the signal over background ratio
$S/B$ at a 100 TeV collider as a function of the ANN output cut $y_{\rm cut}$
for the three categories are shown in 
Fig.~\ref{fig:sb_mva}.
%
We have assumed a total integrated luminosity of $\mathcal{L}=10$ ab$^{-1}$, and only the
irreducible QCD $4b$ background is included.
%
The values 
for $y_{\rm cut}=0$ correspond to those at
the end of the loose cut-based analysis.
%
We observe how in the three
 categories there is a marked  improvement both in signal
 significance and in the signal over
 background ratio as compared to the pre-MVA results.
 %
 In Table~\ref{table:cutflowMVA} we collect
 the post-MVA results for the optimal value of the
    ANN discriminant $y_{\rm cut}$ in the three categories, compared with the
    corresponding
    pre-MVA results ($y_{\rm cut}=0$).
    %
    We also quote the number of signal and
    background events expected for an integrated
    luminosity of $\mathcal{L}=10$ ab$^{-1}$.

@@

From Fig.~\ref{fig:sb_mva} and Table~\ref{table:cutflowMVA} we observe that the statistical
significance of the three categories is very large, with a post-MVA value of
$S/\sqrt{B}\simeq 20$ in the boosted
category.
%
However, we also find that as compared to 14 TeV, the QCD multijet background increases
more rapidly than the signal, and thus $S/B$ is actually smaller than at 14 TeV~\cite{Behr:2015oqq}.
%
Achieving  percent values in $S/B$ requires a very hard cuts on the value of the ANN output.
%
We observe that at 100 TeV the boosted category is the most promising one: not only
it benefits from the highest signal significances, it also exhibits
the best signal over background ratio.
%
Let us recall that at 14 TeV instead~\cite{Behr:2015oqq}  the higher significance was obtained with the resolved category.
%
Unfortunately, as we discuss below, the boosted category is the less sensitive to the Higgs self-coupling,
and thus a measurement of the trilinear will depend to good extent on the resolved category.
%
Therefore, at a 100 TeV collider, even more that at 14 TeV, the feasibility of the measurement
of $\sigma(hh\to b\bar{b}b\bar{b})$ depends strongly on how small the systematic
uncertainties can be, in particular for the background determination.

\paragraph{Extracting the Higgs self-coupling.}
%
The extraction of the trilinear coupling $\lambda$ from the
  corresponding cross-section is complicated by the
  destructive interference
  between diagrams that depend on $\lambda$ and those that do not.
  %
 Here we provide a first estimate of the accuracy
  in Higgs self-coupling extraction from the $b\bar{b}b\bar{b}$ final state
  that can be achieved at a 100 TeV hadron collider.
  %
  A robust estimate  would require
  a careful study of the impact of
  experimental systematic uncertainties, which is beyond the scope of this contribution.
  %
  Therefore, we will use a number of simplifying assumptions, in particular
  a very simple estimate of the total systematic uncertainty in the cross-section
  measurement, which is the limiting factor in the extraction of $\lambda$.

  The sensitivity in the Higgs self-coupling is defined by the $\chi^2$ estimator
  \be
  \label{eq:chi2profile}
  \chi^2(\lambda) \equiv \frac{\lc \sigma(hh,\lambda) - \sigma(hh,\lambda_{\rm SM})
    \rc^2}{\lp \delta_{\rm stat}\sigma\rp^2+\lp \delta_{\rm sys}\sigma\rp^2 } \, ,
  \ee
  where $\lambda$ is the Higgs
  self-coupling, $\lambda_{\rm SM}$ is the SM value, $\sigma(hh,\lambda)$ is the
  post-MVA signal cross-section for a given value of $\lambda$, and $\delta_{\rm stat}\sigma$ and
  $\delta_{\rm sys}\sigma$ are respectively the statistical and systematic uncertainties in the cross-section
  measurement.
  %
  Signal samples for a range of $\lambda$ values have been  processed
  by the same analysis chain, including the MVA (which is not
  retrained), than the SM samples.
  %
  The 68\% CL range for the extraction of $\lambda$ can then be found using
  the usual parameter-fitting criterion by determining the values $\pm \delta\lambda$
  for which the cross-section satisfies
  \be
  \label{eq:condition}
\chi^2(\lambda_{\rm SM}~^{+\delta\lambda}_{-\delta\lambda})=\chi^2(\lambda_{\rm SM})+1 \, .
\ee
%
The final result for the accuracy in the trilinear extraction can be obtained by combining
in quadrature the separate results
from the three exclusive categories.

In Fig.~\ref{fig:chi2} we show the $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section at
  various steps of the cut-flow, including after $b$-tagging
  (before MVA) and after the MVA, in the resolved (left plot)
  and boosted (right plot) categories,  as a function of the Higgs self-coupling
  $\lambda/\lambda_{\rm SM}$ in units of the SM coupling.
  %
  See~\cite{Behr:2015oqq} for the definition of the different steps
  in the analysis chain.
  %
  We find that, despite that fact that the MVA is only trained on the SM sample, the signal
  selection efficiency of the MVA is relatively flat when $\lambda$ is varied, reflecting the fact
  that the signal kinematics do not change dramatically.
  %
  We also see that the resolved category (low and medium Higgs $p_T$) is more sensitive to variations of $\lambda$ than
  the boosted one (large Higgs $p_T$), as indicated by the shallower minimum of the latter after the MVA.
  %
  This reflects the well-known fact that the triangle diagram (which depends on the Higgs self-coupling) is
  dominant near the threshold region.

@@

 %
  Imposing the condition Eq.~(\ref{eq:condition}) we can derive the 68\% confidence level intervals
  on the Higgs self-coupling $\lambda_{\rm min}/\lambda_{\rm SM}$ (in units of the SM value) in the boosted, resolved and intermediate categories, for  different assumptions on the total systematic error in the measured
  cross-section.
  %
  The ranges that are found are reported in Table~\ref{tab:chi2}.
  %
  As expected, the results depend very strongly on the assumption for the systematic uncertainty
  on the measured cross-section.
  %
  In the optimistic scenario of a measurement with $\delta_{\rm sys}\sigma=25\%$,
  the best performance comes from the resolved category, where at the 68\% CL the trilinear
  can be determined to lie in the interval $\lambda/\lambda_{SM}\in \lc 0.9, 1.5\rc$.
  %
  Looser constrains are derived from the intermediate and specially from the boosted category.
  %
  On the other hand, for $\delta_{\rm sys}\sigma=100\%$, the constraints in all three categories
  become very loose, specially for $\lambda/\lambda_{\rm SM}\ge 1$, due to the negative interference effects.

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|}
    \hline
  $\lc \lambda_{\rm min}/\lambda_{\rm SM},\lambda_{\rm max}/\lambda_{\rm SM} \rc$  &  $\delta_{\rm sys}\sigma=25\%$ & $\delta_{\rm sys}\sigma=100\%$ \\
    \hline
    \hline
Boosted   & $\lc -0.1, 2.2\rc$  & $\lc -1.5, > 9\rc$  \\
\hline
Intermediate   & $\lc 0.7, 1.6\rc$  &  $\lc -0.4, > 9\rc$  \\
\hline
Resolved   & $\lc 0.9, 1.5\rc$  &  $\lc -0.1, 7\rc$  \\
\hline
  \end{tabular}
  \caption{\small \label{tab:chi2} The 68\% confidence level intervals
    on the Higgs self-coupling $\lambda_{\rm min}/\lambda_{\rm SM}$ (in units of the SM value)
    obtained from the condition
    Eq.~(\ref{eq:condition}) in the boosted, resolved and intermediate categories.
    %
    We consider two different assumptions on the total systematic error in the measured
    cross-section,  $\delta_{\rm sys}=25\%$ and $\delta_{\rm sys}=100\%$.
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Summary.} In this contribution we have performed a first exploration of the accuracy that can be expected
for the extraction of the Higgs self-coupling at a 100 TeV hadron collider using the $b\bar{b}b\bar{b}$ final state.
%
We find that while the statistical significance of the measurement of the $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section
is very large, the $S/B$ ratio is quite low (and in particular worse than at 14 TeV),
specially in the resolved category, the one with the highest sensitivity
to the self-coupling.
%
This is a consequence of the fact that from 14 TeV to 100 TeV the QCD multijet background increases more rapidly than
the di-Higgs signal.
%
Our estimate of the expected precision on the Higgs trilinear depends strongly on the assumptions
about the experimental systematics.
%
For a measurement with a 25\% systematic uncertainty, the self-coupling can be determined
with accuracy $^{+50\%}_{-10\%}$ at the 68\% CL using the resolved category, but these constraints become substantially
looser if the systematic uncertainties are increased.
